Efficiently Detecting Intrusions\\in the Internet of Things

### 2014-09-29 paper.tex
rewrote title and abstract

\title{A Domain Specific Language for Functional Code Fusion for
       Intrusion Detection Algorithms in Wireless Sensor Networks}

@@

Introducing intrusion detection in wireless sensor network (WSNs) puts a strain
on the limited resources of its nodes. Fusion of the underlying algorithms can
alleviate this, but the manual and repetitive labor proves to be an
unacceptable economic burden and is error-prone. Intrusion detection algorithms
share common functionality and structure, and therefore are a prime candidate
for the application of a domain specific language (DSL). In this paper we
propose such a DSL to describe these algorithms in a formal and functional way.
This allows for the automation of the fusion of these algorithms on a
functional level though code generation. The code, produced by a prototype code
generator implementation, shows to have less impact on e.g. the execution time
of the resulting intrusion detection system and its use of the wireless
network, in comparison with a basic side-by-side implementation of the same
algorithms.

>>>>

\title{Efficiently Detecting Intrusions\\in the Internet of Things}

@@

Supporting multiple intrusion detection (ID) algorithms imposes significant
overhead on Internet of Things (IoT) devices. Fusion of the underlying
algorithms can alleviate this, yet, proves to be time-consuming, repetitive and
error-prone. To address this problem we introduce id-foo, a framework for the
development of efficient intrusion detection systems (IDS). It consists of a
domain specific language (DSL) that allows describing ID algorithms in a formal
and functional way. The id-foo code generator then fuses these algorithms on a
functional level and produces more optimally organised source code. A
side-by-side comparison shows that id-foo-based code significantly reduces
memory footprint, message passing overhead and execution time in comparison to
a straightforward and sequential implementation of the same algorithms.
